Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-02-14 Paper.tex
Update Paper.tex

The machine does not follow the standard von Neumann architecture. Rather than storing program code in generally-accessible memory or storage, it is stored separately in a virtual ROM interactable only through a specialised instruction.

The machine can have exceptional execution for several reasons, including stack underflows and invalid instructions. Like the out-of-gas (OOG) exception, they do not leave state changes intact. Rather, the machine halts immediately and reports the issue to the execution agent (either the transaction processor or, recursively, the spawning execution environment) which will deal with it separately.

>>>>

La macchina non aderisce allo standard di architetttura Neumann. Piuttosto che memorizzare il codice del programma in una memoria o storage generalmente accessibile, esso è memorizzato seperatamente in una ROM virtuale modificabile soltanto attraverso un'istruzione specializzata.

La macchina può avere un'esecuzione eccezionale per diversi motivi, including stack underflows and invalid instructions. Like the out-of-gas (OOG) exception, they do not leave state changes intact. Rather, the machine halts immediately and reports the issue to the execution agent (either the transaction processor or, recursively, the spawning execution environment) which will deal with it separately.
